Secontrails plots

### 2022-01-17 R/Secontrails plots.Rmd

# Plots
```{r}
ggplot() +
  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "P6 zones exploitables") +

@@

  # Tree selection
  # geom_sf(data = NonHarvestable,
  #         aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  # geom_sf(data = Future,
  #         aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  # geom_sf(data = HarvestableUp,
  #         aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  # geom_sf(data = ProbedHollow,
  #         aes(colour = "Probed hollow"), show.legend = "point") +
  geom_sf(data = MainTrails) +

  scale_colour_manual(values = c("Non-harvestable" = "grey",
                                 "Visible defect" = "pink", "Harvestable" = "skyblue",
                                 "HarvestableUp" = "blue", "Selected" = "red", "Future" = "orange",
                                 "Reserve" = "purple", "Probed hollow" = "forestgreen")) +
  labs(color = "Logging status") +
  labs(title = "P16 EFI3")
```

>>>>

# Plots
```{r}
ggplot() +
  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "Paracou P6 zones exploitables") +

@@

  # Tree selection
  # geom_sf(data = NonHarvestable,
  #         aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  geom_sf(data = Future,
          aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  # geom_sf(data = HarvestableUp,
  #         aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  # geom_sf(data = ProbedHollow,
  #         aes(colour = "Probed hollow"), show.legend = "point") +
  geom_sf(data = MainTrails) +

  scale_colour_manual(values = c("Non-harvestable" = "grey",
                                 "Visible defect" = "pink", "Harvestable" = "skyblue",
                                 "HarvestableUp" = "blue", "Selected" = "red", "Future" = "orange",
                                 "Reserve" = "purple", "Probed hollow" = "forestgreen")) +
  labs(color = "Logging status") +
  labs(title = "Paracou P16 EFI3")
```
